Fourmile_inputs

### 2022-10-03 fourmile_inputs.Rmd
added updated solar gap filling

#rh done
write.csv(rhall, 'rh_use.csv')

@@

write.csv(windall, 'wind_use.csv')

@@

write.csv(tmaxall, 'tmax_use.csv')

@@

#check the date range, make sure tip bucekts are being used at right times
# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
#   replace(is.na(.), -9999) %>%
#   dplyr::select(-c(doy))

@@

>>>>

#rh done
#write.csv(rhall, 'rh_use.csv')

@@

#write.csv(windall, 'wind_use.csv')

@@

#write.csv(tmaxall, 'tmax_use.csv')

@@

@@

# combine all met data together

wind <- read_csv('wind_use.csv')
sol <- read_csv('solar_use.csv')
tmin <- read_csv('tmin_use.csv')
tmax <- read_csv('tmax_use.csv')
prec <- read_csv('prec_use.csv')
rh <- read_csv('rh_use.csv')

#put all data frames into list
df_list <- list(prec, sol, tmin, tmax, wind, rh)

#merge all data frames in list
met_all <- df_list %>% 
  reduce(full_join, by='date')

met_all <- met_all %>%  
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  replace(.==-9999, NA) %>%
  filter(date > '2009-12-31')

met_fill <- missRanger(met_all, num.trees=1000)

solar <- ggplot(met_fill, aes(x=date)) +
  geom_line(aes(y=Gordon_S_mjm2), color='blue') +
  geom_line(aes(y=Niwot_mjm2), color='red') +
  geom_line(aes(y=Betasso_mjm2), color='orange')

ggplotly(solar)
